Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-09 paper.tex
Adds emails

%%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
\title{Enhancing the sales prediction of newly published books by means of computational intelligence methods}

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
\author {
P.A. Castillo$^1$, A.M. Mora$^1$, H. Faris$^2$, J.J. Merelo$^1$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
}
\institute{
$^1$Department of Computer Architecture and Computer Technology. CITIC, ETSIIT. University of Granada (Spain)\\
$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
           e-mail: {\tt pacv@ugr.es}
}

>>>>

%%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
\title{Enhancing the prediction of sales for newly published books by
  means of computational intelligence methods}

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
\author {
P.A. Castillo$^1$, A.M. Mora$^1$, H. Faris$^2$, J.J. Merelo$^1$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
}
\institute{
$^1$Department of Computer Architecture and Computer Technology. CITIC, ETSIIT. University of Granada (Spain)\\
$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
e-mail: {\tt pacv@ugr.es, amorag@geneura.ugr.es,
  jmerelo@geneura.ugr.es, pgarcia@geneura.ugr.es,
  antares.es@gmail.com, mgarenas@ugr.es, palomacd@ugr.es}
}
